Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-29 cogsci2016/paper.tex
figure
discussion

	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}: 
	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
	between overlapping phases of behavior with tools and objects, which have been called overlapping waves \cite{siegler1996emerging}. 
	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
	[more details?]

@@

			%\begin{figure}[t]
				%\center
				%\input{include/F.tikz}
				%\vspace{-0.25cm}
				%\input{include/H1.tikz}
				%\vspace{-0.5cm}
				%\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
				%\label{Architectures}					
			%\end{figure}

@@

	Also, for each condition we measure the total exploration of the different sensory spaces during training. 
	The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
	in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
	The exploration of the boxes is the number of boxes that have been filled with the object during training.
	Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
	We provide statistical Mann-Whitney U test results of comparisons of the exploration in different pairs of conditions.
	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
	Then, F-RGB explores all spaces less than H-RGB-RMB condition ($p<0.01$).
	Also, H-RGB-GR-AMB shows lower exploration all spaces than H-RGB-P-AMB ($p<0.01$).
	Condition H-RGB-P-AMB-PGITC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB, and difference is not significant in other spaces.

	\begin{figure*}[ht]
		\centering
		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
		\vspace{-0.4cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
		\subfloat[$Boxes$]{\includegraphics[width=3.3cm]{./include/xp1-explo-box.pdf}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}

@@

>>>>

	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}, \cite{fenson1976developmental}: 
	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
	between overlapping phases of behavior with tools and objects, which have been called overlapping waves \cite{siegler1996emerging}. 
	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
	[more details?]

@@

			\begin{figure}[t]
				\center
				\input{include/F.tikz}
				\vspace{-0.25cm}
				\input{include/H1.tikz}
				\vspace{-0.5cm}
				\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
				\label{Architectures}					
			\end{figure}

@@

	Also, for each condition we measure the total exploration of the different sensory spaces during training. 
	The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
	in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
	The exploration of the boxes is the number of boxes that have been filled with the object during training.
	Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
	We provide statistical Mann-Whitney U test results of comparisons of the exploration in different pairs of conditions.
	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
	Then, F-RGB explores all spaces less than H-RGB-RMB condition ($p<0.01$).
	H-RGB-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-RGB-P-AMB.
	Also, H-RGB-GR-AMB shows lower exploration all spaces than H-RGB-P-AMB ($p<0.01$).
	Condition H-RGB-P-AMB-PGITC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB, and difference is not significant in other spaces.

	\begin{figure*}[ht]
		\centering
		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
		\vspace{-0.4cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
		\subfloat[$Boxes$]{\includegraphics[width=3.3cm]{./include/xp1-explo-box.pdf}}
		\caption{Exploration of sensory spaces. Box plots show for each condition and space the median and quartiles of the $100$ trials.}
		\label{res_explo}
	\end{figure*}

@@

		Results show that random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
		but random model babbling explores slightly less the object position.
		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level, 
		because here all models are still useful to explore.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.
